UKB Models

### 2023-10-03 ukb_mods.Rmd
code to find sex terms in fitted mods

#split by measure type (Vol, SA, CT)
vol_list <- col_list[grepl("^lh_Vol|^rh_Vol|^GMV$|^WMV$|^sGMV$|^Ventricles$", col_list)]
writeLines(vol_list, con = "pheno_lists/Vol_list.txt")

@@

@@

```

>>>>

#split by measure type (Vol, SA, CT)
vol_list_global <- c("GMV", "sGMV", "WMV", "Ventricles")
writeLines(vol_list_global, con = "pheno_lists/Vol_list_global.txt")

vol_list_regions <- col_list[grepl("^lh_Vol|^rh_Vol", col_list)]
writeLines(vol_list_regions, con = "pheno_lists/Vol_list_regions.txt")

@@

```{r}
ggplot(data=ukb_df_totals, aes(x=age_days, y=Vol_total)) +
  geom_point(aes(color=sex), alpha=0.6, position="identity")

ggplot(data=ukb_df_totals, aes(x=age_days, y=TBV)) +
  geom_point(aes(color=sex), alpha=0.6, position="identity") #TBV includes ventricles, WMV, subcortical GMV

ggplot(data=ukb_df_totals, aes(x=age_days, y=CT_total)) +
  geom_point(aes(color=sex), alpha=0.6, position="identity")

ggplot(data=ukb_df_totals, aes(x=age_days, y=SA_total)) +
  geom_point(aes(color=sex), alpha=0.6, position="identity")
```

@@

formula(lh_SA_middletemporal_mod, what="sigma")
coef(lh_SA_middletemporal_mod, what="sigma") %>%
  names()

sfit <- summary(lh_SA_middletemporal_mod)

sfit$coef.table

#to get a list of all the slots in the object
str(sfit)
```
